\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[total={6.5in, 9in}, heightrounded]{geometry}
\usepackage{hyperref}

\hypersetup
{
	colorlinks = true,
	allcolors = OliveGreen
}

\graphicspath{{graphics/}}
\setenumerate[0]{label=\alph*)}
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}
\setlength\fboxsep{0pt}
\renewcommand{\baselinestretch}{1.6}
\titleformat{\section}
{\normalfont \Large \bfseries \centering}{}{0pt}{}

\newcommand{\s}[1]{{\color{violet} #1}}



\begin{document}\Large Name: \rule{2in}{0.15mm} \hfill Homework 3 | Math 256 | Cruz Godar \vspace{4pt}  \large

\textit{Due Wednesday of Week 4 at the start of class}

Complete the following problems and submit them as a pdf to Canvas. 8 points are awarded for thoroughly attempting every problem, and I'll select three problems to grade on correctness for 4 points each. Enough work should be shown that there is no question about the mathematical process used to obtain your answers.

<button class="text-button" type="button" id="download-homework-3-pdf-button" tabindex="-1"></button><button class="text-button" type="button" id="download-homework-3-tex-button" tabindex="-1"></button>
\section{Section 3}

In problems 1--3, find the indicated derivative.

1. $\displaystyle \frac{\partial }{\partial t} \left[ 2ty + \sin(t) \right].$

2. $\displaystyle \frac{\partial }{\partial y} \left[ \sin(xy^x) \right].$

3. $\displaystyle \frac{\partial }{\partial x} \left[ \sin(xy^x) \right].$

~\\

4. Using the multivariable chain rule, find $\displaystyle \frac{d f(x, y)}{dt}$, where $\displaystyle f(x, y) = 2x^2 + \sec(xy^2)$, $x(t) = t$, and $y(t) = 5t^2$.

~\\

In problems 5--7, find the indicated integral. Make sure to express the constant as a function of the correct variable.

5. $\displaystyle \int f(x, y)\,\mathrm{d} x$ for $\displaystyle f(x, y) = 2x\cos(y - x).$

6. $\displaystyle \int f(x, y)\,\mathrm{d} y$ for $f$ as in the previous problem.

7. $\displaystyle \int g(x, y)\,\mathrm{d} y$ for $\displaystyle g(x, y) = e^{x^2}.$

~\\

In problems 8--14, solve the the given DE.

8. $\displaystyle 2y + 1 + (2x + 1)y' = 0,$ $\displaystyle y(1) = 1.$

9. $\displaystyle 1 - \sin(t + y) + y'(-\sin(t + y)) = 0,$ $\displaystyle y(0) = 0.$

10. $\displaystyle \sin(y)y' - te^t\cos(y) = 0.$

11. $\displaystyle y' = -\frac{yx^{y - 1}}{x^y\log(x)},$ $\displaystyle y(2) = 1.$

12. $\displaystyle ty' + y + t^{-2} = 0,$ $\displaystyle y(2) = 2.$

13. $\displaystyle (10t + t^2) - 2\sin(y)y' = 0,$ $\displaystyle y(0) = 1.$

14.

$$
	\sec^2(x)\sec(y) + \left( \tan(x) \tan(y) \sec(y) + \frac{1}{y} \right)y' = 0.
$$


\end{document}