\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[total={6.5in, 9in}, heightrounded]{geometry}
\usepackage{hyperref}

\graphicspath{{graphics/}}
\setenumerate[0]{label=\alph*)}
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}
\setlength\fboxsep{0pt}
\renewcommand{\baselinestretch}{1.6}
\titleformat{\section}
{\normalfont \Large \bfseries \centering}{}{0pt}{}

\newcommand{\s}[1]{{\color{violet} #1}}

\begin{document}

\Large Name: \rule{2in}{0.15mm} \hfill Homework 3 | Math 253 | Cruz Godar \vspace{4pt} \normalsize

\textit{Due Wednesday of Week 4 at the start of class}

Complete the following problems and submit them as a pdf to Canvas. 8 points are awarded for thoroughly attempting every problem, and I'll select three problems to grade on correctness for 4 points each. Enough work should be shown that there is no question about the mathematical process used to obtain your answers.

~\\

In problems 1--6, determine if the series converges.

1. $\displaystyle \sum_{m = 1}^\infty \frac{n}{n^2 + 1}$.

2. $\displaystyle \sum_{n = 1}^\infty \frac{1}{\sqrt{n}}$.

3. $\displaystyle \sum_{k = 1}^\infty \sin(k)$.

4. $\displaystyle \sum_{n = 2}^\infty \frac{1}{n \sqrt{n^2 - 1}}$.

5. $\displaystyle \sum_{n = 2}^\infty \frac{1}{n\ln{n}}$.

6. $\displaystyle \sum_{m = 1}^\infty \frac{\ln(m)}{m^2}$.

~\\

7. For each of the series in problems 1--6 that converges, find a value of $N$ so that the $N$th remainder $R_N$ is below $0.01$. Then compute the $N$th partial sum of the series with a tool like \href{https://wolframalpha.com}{WolframAlpha}.

~\\

8. You want to play a game with a fair 4-sided die (one with labels 1--4, each with an equal chance of being rolled). However, you only have a 6-sided die. If you roll the 6-sided die and reroll it whenever you get a 5 or 6 until you get a number between 1 and 4, is this equivalent to a 4-sided die?

9. Is there a way to use only a 6-sided die to emulate a 12-sided one? What about an 8-sided one? A 7-sided one?


\end{document}