\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[total={6.5in, 9in}, heightrounded]{geometry}
\usepackage{hyperref}

\graphicspath{{graphics/}}
\setenumerate[0]{label=\alph*)}
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}
\setlength\fboxsep{0pt}
\renewcommand{\baselinestretch}{1.6}
\titleformat{\section}
{\normalfont \Large \bfseries \centering}{}{0pt}{}

\newcommand{\s}[1]{{\color{violet} #1}}

\begin{document}

\Large Name: \rule{2in}{0.15mm} \hfill Homework 1 | Math 342 | Cruz Godar \vspace{4pt} \normalsize

\textit{Due Wednesday of Week 2 at the start of class}

Complete the following problems and submit them as a pdf to Canvas. 8 points are awarded for thoroughly attempting every problem, and I'll select three problems to grade on correctness for 4 points each. Enough work should be shown that there is no question about the mathematical process used to obtain your answers.

\section{Section 0}

In problems 1--3, do the following:

\begin{enumerate}

	\item Write the system of equations in the form $A\vec{x} = \vec{b}$ for a matrix $A$ and a vector $\vec{b}$ of constants, and a vector $\vec{x}$ of variables.

	\item Augment $A$ with $\vec{b}$ and row reduce the system to solve for $\vec{x}$.

	\item If $A$ is square, find $\det A$.

	\item Let $T$ be the linear transformation corresponding to the matrix $A$. Write down the domain and codomain for $T$.

	\item Find a basis for $\ker T$ and use it to find a basis for $\operatorname{image} T$ using the fundamental theorem of linear algebra.

	\item Determine if $T$ is one-to-one, onto, both, or neither. If it's both one-to-one and onto, find a formula for $T^{-1}$.

\end{enumerate}

1.

\begin{align*}
	x + y &= 1\\
	x - y &= 3
\end{align*}

2.

\begin{align*}
	x + 2y - z &= -1\\
	2x + 3y - w &= -2
\end{align*}

3.

\begin{align*}
	x + y + 2z &= 4\\
	2x + y - z &= 2\\
	-3x - y + 4z &= 0
\end{align*}

~\\

In problems 4--7, do the following:

\begin{enumerate}

	\item The given sets $V$ and $W$ are vector spaces. Determine whether the subset $X$ of $V$ is a subspace. If it is, show it satisfies all three subspace properties, and if not, give a specific example showing one of the properties fails.

	\item Determine whether the function $T : V \to W$ is a linear transformation. If it is, show it satisfies the two properties, and if not, give a specific example showing one of them fails.

	\item If $T$ is a linear transformation, find the matrix for $T$ with respect to the standard bases for $V$ and $W$.

	\item If $T$ is a linear transformation, find a basis for $\ker T$ and use it to find bases for $V$ and $\operatorname{image} T$ using the fundamental theorem of linear algebra. Then extend the basis for $\operatorname{image} T$ to a basis for $W$, and find the matrix for $T$ with respect to the bases for $V$ and $W$ you found.

\end{enumerate}

4. $V = \mathbb{R}^4$, $W = M_{2 \times 2}(\mathbb{R})$, $X$ is the set of vectors $\left[\begin{array}{c} x \\ y \\ z \\ w \end{array}\right] \in \mathbb{R}^4$ such that $x + 2y = w$, and $T : V \to W$ is defined by

\begin{align*}
	T\left( \left[\begin{array}{c} x \\ y \\ z \\ w \end{array}\right] \right) = \left[\begin{array}{cc} 0& x \\ y + z& 2w \end{array}\right].
\end{align*}

5. $V = M_{2 \times 2}(\mathbb{R})$, $W = M_{2 \times 2}(\mathbb{R})$, $X$ is the set of matrices $A$ such that $\det A = 0$, and $T : V \to W$ is defined by

$$
	T(A) = A^T,
$$

where $A^T$ is the \textbf{transpose} of $A$, defined by $(A^T)_{ij} = A_{ji}$ (it effectively flips $A$ across its diagonal).

6. $V$ is the space of polynomials with degree at most 3, $W = \mathbb{R}^2$, $X$ is the set of polynomials $p(x)$ such that $p'(x) = 1$, and $T : V \to W$ is defined by

$$
	T(a + bx + cx^2 + dx^3) = \left[\begin{array}{c} a + b \\ c + d \end{array}\right].
$$

7. $V = \mathcal{L}(\mathbb{R}, \mathbb{R}^2)$, $W = M_{2 \times 2}(\mathbb{R})$, $X$ is the set of linear transformations $S : \mathbb{R} \to \mathbb{R}^2$ such that $S(1) = \left[\begin{array}{c} 0 \\ 0 \end{array}\right]$, and $T : V \to W$ is defined by

\begin{align*}
	T(S) = \left[\begin{array}{cc} \mid& \mid \\ S(1)& S(-1) \\ \mid& \mid \end{array}\right],
\end{align*}

i.e. the outputs of $S$ are placed as columns in a $2 \times 2$ matrix.

\section{Section 1}

In problems 8--10, find the eigenvalues and eigenvectors of the matrix.

8. $A = \left[\begin{array}{cc} 2& -1 \\ 3& -2 \end{array}\right]$.

9. $B = \left[\begin{array}{cc} -1& 2 \\ 0& -3 \end{array}\right]$.

10. $C = \left[\begin{array}{ccc} 2& 2& -2 \\ -3& 7& 3 \\ -5& 5& 5 \end{array}\right]$.

~\\

11. Let $A = [a_{ij}]$ be an $n \times n$ matrix that is upper triangular --- that is, $a_{ij} = 0$ whenever $i > j$. What are the eigenvalues of $A$ in terms of the entries $a_{ij}$? Justify your answer.

12. Let $A$ be an $n \times n$ matrix with eigenvectors $\vec{v_1}, ..., \vec{v_n}$ and corresponding eigenvalues $\lambda_1, ..., \lambda_n$. If $A$ is invertible, what are the eigenvectors and eigenvalues of $A^{-1}$? Justify your answer.

13. Let $A$ be an $n \times n$ matrix with eigenvalues $\lambda_1, ..., \lambda_n$. What are the eigenvalues of $A^T$? Justify your answer.


\end{document}