\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[total={6.5in, 9in}, heightrounded]{geometry}
\usepackage{hyperref}

\graphicspath{{graphics/}}
\setenumerate[0]{label=\alph*)}
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}
\setlength\fboxsep{0pt}
\renewcommand{\baselinestretch}{1.6}
\titleformat{\section}
{\normalfont \Large \bfseries \centering}{}{0pt}{}

\newcommand{\s}[1]{{\color{violet} #1}}

\begin{document}

\Large Name: \rule{2in}{0.15mm} \hfill Homework 7 | Math 253 | Cruz Godar \vspace{4pt} \normalsize

\textit{Due Wednesday of Week 8 at the start of class}

Complete the following problems and submit them as a pdf to Canvas. 8 points are awarded for thoroughly attempting every problem, and I'll select three problems to grade on correctness for 4 points each. Enough work should be shown that there is no question about the mathematical process used to obtain your answers.

~\\

In problems 1--3, find a power series for the function using power series multiplication and determine its interval of convergence.

1. $\displaystyle \left( \frac{1}{1 - x} \right)\left( \frac{1}{1 + x} \right)$.

2. $\displaystyle \left( \frac{1}{1 - x} \right)\left( \frac{1}{(1 + x)^2} \right)$.

3. $\displaystyle \left( \frac{1}{(1 - x)^2} \right)\left( \frac{1}{(1 + x)^2} \right)$.

~\\

In problems 4--5, find a power series for the given function using calculus and determine its interval of convergence.

4. $\displaystyle \ln\left( 1 + x^2 \right)$.

5. $\displaystyle \frac{1}{(1 + 2x)^4}$.

~\\

6. Let $\displaystyle f(x) = \sum_{n = 0}^\infty c_n x^n$ on $(-R, R)$, so that the series does not converge at $x = R$. Is it possible for the series for $f'(x)$ to converge at $x = R$? Give an example of a series where this is true or justify why no such series can exist.

7. Let $\displaystyle f(x) = \sum_{n = 0}^\infty c_n x^n$ on $(-R, R)$, so that the series does not converge at $x = R$. Is it possible for the series for $\displaystyle \int f(x)\,\text{d} x$ to converge at $x = R$? Give an example of a series where this is true or justify why no such series can exist.

~\\

8. Let $f(x) = \sin(x)$.

\begin{enumerate}

	\item What are $f(0)$ and $f'(0)$?

	\item Suppose $\displaystyle f(x) = \sum_{n = 0}^\infty c_n x^n$. What are $c_0$ and $c_1$?

	\item Since $f''(x) = -\sin(x) = -f(x)$, the coefficient sequence $(c_n)$ satisfies a recurrence. Write that recurrence down.

	\item Find an explicit formula for $c_n$. (Hint: handle even and odd $n$ separately).

	\item What is the interval of convergence for $\displaystyle \sum_{n = 0}^\infty c_n x^n$?

\end{enumerate}


\end{document}