\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[total={6.5in, 9in}, heightrounded]{geometry}
\usepackage{hyperref}

\graphicspath{{graphics/}}
\setenumerate[0]{label=\alph*)}
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}
\setlength\fboxsep{0pt}
\renewcommand{\baselinestretch}{1.6}
\titleformat{\section}
{\normalfont \Large \bfseries \centering}{}{0pt}{}

\newcommand{\s}[1]{{\color{violet} #1}}

\begin{document}

\Large Name: \rule{2in}{0.15mm} \hfill Homework 2 | Math 256 | Cruz Godar \vspace{4pt} \normalsize

\textit{Due Wednesday of Week 3 at the start of class}

Complete the following problems and submit them as a pdf to Canvas. 8 points are awarded for thoroughly attempting every problem, and I'll select three problems to grade on correctness for 4 points each. Enough work should be shown that there is no question about the mathematical process used to obtain your answers.

\section{Section 2}

In problems 1--10, solve the DE. Whenever possible, fully evaluate all integrals.

1. $\displaystyle y' + 2y = e^{-2t},$ $\displaystyle y(0) = -1.$

2. $\displaystyle y' + \frac{y}{t} = \sin(t),$ $\displaystyle y(\pi) = 0.$

3. $\displaystyle xy' = \sqrt{y^2x^2 - y^2}.$ Hint: during the integration, you'll want to set $x = \sec(\theta)$ and use trig sub.

4. $\displaystyle y' = y + t^2e^t.$

5. $\displaystyle y' = \frac{t}{1 + y},$ $\displaystyle y(0) = -2.$

6. $\displaystyle y' + ty^2 + ty + 2y^2 + 2y = 0.$

7. $\displaystyle ty' + (t + 1)y = t + 2,$ $\displaystyle y(1) = 2.$

8. $\displaystyle \cos^2(t)y' = 1 + y.$

9. $\displaystyle y' = t + \frac{t}{y}.$

10. $\displaystyle y' = e^{x + y},$ $\displaystyle y(0) = 0.$

~\\

11. You invest $\$1000$ into an account which compounds interest \textbf{continuously} --- in other words, your balance is constantly increasing at a rate proportional to its current value. If the continuous interest rate is $0.2\%$ per year, how much money will be in the account after 10 years?

~\\

12. The population $P(t)$ of a colony of bacteria after $t$ hours (in thousands) follows the equation $\displaystyle P' + P = 2^{-t} + 1.$ After enough time, what will the population settle down to?

~\\

13. The function $y$ satisfies $y' = y\log(x)$ with $\displaystyle y(1) = \frac{1}{e}.$

\begin{enumerate}

	\item Express $y''$ in terms of $x, y$, and $y'$.

	\item Solve the original DE, find $y''$ in terms of $x$ only, and verify that your answer to part a) was correct.

\end{enumerate}

~\\

14. Solve the DE $\displaystyle y' + xy = x$ in two ways: first with integrating factors and then with separation of variables. Make sure your answers are the same!

~\\

15. True or false: if a DE is separable, then its direction field is symmetric about the origin --- i.e. the slope at $(x, y)$ is the same as the slope at $(-x, -y)$. If it's true, briefly explain why, and if it's false, give a counterexample.

~\\

16. A tank is filled with $1\,\text{L}$ of water. We begin pouring in a salt solution with a concentration of $2\,\frac{\text{g}}{\text{mL}}$ at a rate of $10\,\frac{\text{mL}}{\text{s}}$, and also begin draining the tank at a rate of $10\,\frac{\text{mL}}{\text{s}}$. What will the concentration of salt be after an hour?

17. A tank is filled with $100\,\text{L}$ of uncolored paint. We begin pouring in a solution of red paint, which contains $0.5\,\frac{\text{kg}}{\text{L}}$ of dye, at a rate of $1\,\frac{\text{L}}{\text{s}}$. We also begin draining the well-mixed paint from the bottom of the tank at a rate of $1\,\frac{\text{L}}{\text{s}}$. How long will it take for the paint in the tank to have half the concentration of dye that the incoming red paint does?


\end{document}