\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[dvipsnames]{xcolor}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{graphicx}
\usepackage[total={6.5in, 9in}, heightrounded]{geometry}
\usepackage{hyperref}

\graphicspath{{graphics/}}
\setenumerate[0]{label=\alph*)}
\setlength{\parindent}{0pt}
\setlength{\parskip}{8pt}
\setlength\fboxsep{0pt}
\renewcommand{\baselinestretch}{1.6}
\titleformat{\section}
{\normalfont \Large \bfseries \centering}{}{0pt}{}

\newcommand{\s}[1]{{\color{violet} #1}}

\begin{document}

\Large Name: \rule{2in}{0.15mm} \hfill Homework 4 | Math 256 | Cruz Godar \vspace{4pt} \normalsize

\textit{Due Wednesday of Week 5 at the start of class}

Complete the following problems and submit them as a pdf to Canvas. 8 points are awarded for thoroughly attempting every problem, and I'll select three problems to grade on correctness for 4 points each. Enough work should be shown that there is no question about the mathematical process used to obtain your answers.

\section{Section 4}

In problems 1--5, solve the DE and verify that you've found the general solution with the Wronskian.

1. $\displaystyle y'' + 2y' - 3y = 0.$

2. $\displaystyle y'' + 3y' = 0.$

3. $\displaystyle 4y'' - 9y = 0.$

4. $\displaystyle y'' - y' - y = 0.$

5. $\displaystyle y'' = y'.$

~\\

In problems 6--8, solve the initial value problem.

6. $\displaystyle y'' + y' - 20y = 0,$ $\displaystyle y(0) = 9,$ $\displaystyle y'(0) = 18.$

7. $\displaystyle 2y'' + 6y' = 20y,$ $\displaystyle y(0) = 14,$ $\displaystyle y'(0) = 0.$

8. $\displaystyle y'' - y = 0,$ $\displaystyle y(0) = 4,$ $\displaystyle y'(0) = 2.$

~\\

9. Consider the DE $\displaystyle 2t^2y'' - ty' + y = 0.$

\begin{enumerate}

	\item Show that a solution is $\displaystyle y = c_1t + c_2\sqrt{t}.$

	\item Compute $\displaystyle W\left[t, \sqrt{t}\right].$ For which value $t = t_0$ is it zero?

	\item Why is $t = t_0$ a problem?

\end{enumerate}

~\\

10. Let $y = a(t) + b(t)i$ be a solution to

$$
	y'' + p(t)y' + q(t)y = 0,
$$

where $a$, $b$, $p$, and $q$ are all real-valued functions. Show that both $a$ and $b$ must be solutions to $y'' + p(t)y' + q(t)y = 0$ themselves.

~\\

11. Consider the DE $\displaystyle y'' - yy' = 0.$

\begin{enumerate}

	\item Show that both $\displaystyle y = \tan\left(\frac{x}{2}\right)$ and $\displaystyle y = 2\tan\left(x + 1\right)$ are solutions.

	\item Show that

\end{enumerate}

$$
	y = c_1\tan\left(\frac{x}{2}\right) + 2c_2\tan\left(x + 1\right)
$$

is \textit{not} a solution in general. Why does this not contradict the results of section 4?


\end{document}